Approximately Exact Calculations for Linear Mixed Models

### 2015-05-21 ms.tex
minor edit

\item[D2] For any box $b$ with sides parallel to the axes we can quickly compute lower and upper bounds $(L^b,U^b)$ satisfying
\begin{equation*}
  L^b \le \inf_{(\sigesq, \sigssq) \in b}\logRLss \qquad\text{and}\qquad
  U^b \ge \sup_{(\sigesq, \sigssq) \in b}\logRLss
\end{equation*}
and such that $U^b-L^b \rightarrow 0$ as $b$ shrinks.  Therefore, partitioning the box $B$ from \textbf{D1} allows us to know $\logRLss$ everywhere in $B$ to within a pre-specified tolerance and also to locate $\argsup\logRL$ to within a pre-specified tolerance without fear of missing regions of high $\logRL$.
\end{description}
\textbf{D1} and \textbf{D2} allow us to divide the $(\sigesq,\sigssq)$ plane into two parts: one where $\logRL$ is low and another where we know $\logRL$ to within a pre-specified $\epsilon$.  The next section shows how the partial derivatives are used to satisfy \textbf{D1} and \textbf{D2}.

>>>>

\item[D2] For any box $b$ with sides parallel to the axes we can quickly compute lower and upper bounds $(L^b,U^b)$ satisfying
\begin{equation*}
  L^b \le \inf_{(\sigesq, \sigssq) \in b}\logRLss \qquad\text{and}\qquad
  U^b \ge \sup_{(\sigesq, \sigssq) \in b}\logRLss
\end{equation*}
and such that $U^b-L^b \rightarrow 0$ as $b$ shrinks.  Therefore, partitioning the box $B$ from \textbf{D1} allows us to know $\logRLss$ everywhere in $B$ to within a pre-specified tolerance and also to locate $\argsup\logRL$ to within a pre-specified tolerance without fear of missing regions of high $\logRL$.
\end{description}
\textbf{D1} and \textbf{D2} allow us to divide the $(\sigesq,\sigssq)$ plane into two parts: one where $\logRL$ is at least $M$ below its maximum and another where we know $\logRL$ to within a pre-specified $\epsilon$.  The next section shows how the partial derivatives are used to satisfy \textbf{D1} and \textbf{D2}.
